Supplementary data for: \\textit{`MSnbase`, efficient and elegant R-based processing and visualisation of raw mass spectrometry data}

### 2020-07-02 large_experiment_processing.Rmd
Update large_experiment_processing.Rmd
Co-authored-by: Sebastian Gibb <mail@sebastiangibb.de>

Next we subset the on-disk object to contain the same set of spectra than the
in-memory `MSnExp` and compare their memory footprint.

@@

Before evaluating the `MSnbase` performance on the large data set we provide
first some general description of the `MSnbase` data classes in `MSnbase` basic
data access operations. MS data from raw data files in mzML, mzXML, mzData or
netCDF format is represented by the `MSnExp` object which organizes the spectra
from the original files in a one-dimensional list. Functions like `rtime` and
`msLevel` allow to extract the retention time and MS level, respectively, for
each spectrum and return a `numeric` (or `integer`) vector with the same length
than the number of spectra in the `MSnExp`. In the example below we use the
`rtime` function to extract the retention times for each spectrum.

>>>>

Next we subset the on-disk object to contain the same set of spectra as the
in-memory `MSnExp` and compare their memory footprint.

@@

Before evaluating the `MSnbase` performance on the large data set we provide
some general description of the `MSnbase` data classes and basic
data access operations. MS data from raw data files in mzML, mzXML, mzData or
netCDF format is represented by the `MSnExp` object which organizes the spectra
from the original files in a one-dimensional list. Functions like `rtime` and
`msLevel` allow to extract the retention time and MS level, respectively, for
each spectrum and return a `numeric` (or `integer`) vector with the same length
than the number of spectra in the `MSnExp`. In the example below we use the
`rtime` function to extract the retention times for each spectrum.
